---
title: "Assignment_3"
author: "Manasa Chelukala"
date: "10/18/2022"
output: pdf_document
---

$$ \text{1) Formulate and solve this transportation problem using R} $$
```{r}
library(lpSolve)
library(lpSolveAPI)
library(tinytex)
```

```{r}
#set the matrix and creating a table
AEDs <- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-"),ncol=5,byrow=TRUE)

colnames(AEDs) <- c("Warehouse1", "Warehouse2", "Warehouse3","Production cost","Production Capacity")
rownames(AEDs) <- c("Plant A", "Plant B", "Monthly Demand")
AEDs <- as.table(AEDs)
AEDs
```
***objective Function:***

$$ \text{The above transportation problem can be formulated in the LP format as below:} $$
$$\text{Miminize} \hspace{.2cm} TC = 622 x_{A1} + 614 x_{A2} + 630 x_{A3} + 0 x_{A4} + 641 x_{B1} + 645 x_{B2} + 649 x_{B3} + 0 x_{B4} $$
$$ \text{Subject to:} $$

$$ \text{Supply constraints} $$

$$  x_{A1} + x_{A2} + x_{A3} + x_{A4}  \le 100 $$ 

$$  x_{B1} + x_{B2} + x_{B3} + x_{B4} \le 120 $$
$$ \text{Demand Constraints:} $$

$$  x_{A1} + x_{B1} \ge 80 $$ 
$$  x_{A2} + x_{B2} \ge 60 $$ 
$$  x_{A3} + x_{B3} \ge 70 $$ 
$$  x_{A4} + x_{B4} \ge 10 $$ 

$$ \text{Non-negativity of the variables:} $$

$$  x_{ij} \ge 0 $$ 

$$ Xij $$ - $$ where represents the number of AEDs shipped from plant i to warehouse j.$$
$$ i = A,B   $$
and
$$  j =1,2,3,4 $$
***I have used R programming language to solve the above transportation cost minimization problem. 
This transportation problem is unbalanced one (demand is not equal to supply), that is demand is less than supply by 10,
so I create a dummy variable in column 4 with transportation cost zero and demand 10.***
 
```{r}
#Creating a matrix for the given objective function
AEDs_Costs <- matrix(c(622,614,630,0,
                       641,645,649,0),ncol = 4,byrow=TRUE)
## Set the names of the rows (constraints) and columns (decision variables)
colnames(AEDs_Costs) <- c("Warehouse1", "Warehouse2", "Warehouse3","Dummy")
rownames(AEDs_Costs) <- c("Plant A", "Plant B")
AEDs_Costs
```

 
```{r}
#setting up constraint signs and right-hand sides(supply side)
row.signs <- rep("<=",2)
row.rhs <- c(100,120)
#Supply function cannot be greater than the specified units

#Demand side constraints#
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)
#Demand function can be greater than the specified units
```

```{r}
#solve the model
lptrans <- lp.transport(AEDs_Costs, "min", row.signs, row.rhs, col.signs, col.rhs)
```

```{r}
#Getting the objective value
lptrans$objval
```
$$ \text{The minimum combined shipping and production costs will be 132,790 dollars based on the given information and constraints.} $$

$$ \text{Next, we will return the values of the decision variables to decide how many units should
be produced and shipped from each plant} $$
```{r}
## Get the optimum decision variables (6)values
lptrans$solution
```
$$ \text{Observations:} $$

Plant A Units Shipped to Warehouse 2: ***60 units ***

Plant A Units Shipped to Warehouse 3: ***40 units***

Plant B Units Shipped to Warehouse 1: ***80 units*** 

Plant B Units Shipped to Warehouse 3: ***30 units***

***and  “10” shows up in the 4th variable it is a “throw-away variable”(dummy).***

***2)Formulate the dual of this transportation problem***

$$ \text{Besides reducing transportation costs, a secondary goal would be to increase value added (VA).} $$

$$ {\text Maximize \hspace{2mm} VA = } \hspace{2mm} 80W_1 + 60W_2 + 70W_3 - 100P_A - 120P_B$$
$$ \text {Subject to the following constraints:} $$

$$ {\text Total \hspace{2mm} Payment \hspace{2mm} Constraints} $$
$$ W_1 - P_A >= 622 $$
$$ W_2 - P_A >= 614$$
$$ W_3 - P_A >= 630$$
$$ W_1 - P_B >= 641$$
$$ W_2 - P_B >= 645$$
$$ W_3 - P_B >= 649$$
\newline
$${\text Where \hspace{2mm} W_1 = Warehouse \hspace{2mm} 1}$$
$$\hspace{2mm} W_2 = Warehouse \hspace{2mm} 2$$
$$\hspace{2mm} W_3 = Warehouse \hspace{2mm} 3$$
$$\hspace{2mm} P_A = Plant \hspace{2mm} 1$$
$$\hspace{2mm} P_B = Plant \hspace{2mm} 2$$
\newline

3)Make an economic interpretation of the dual

$$W_1 \le 622 + P_A $$
$$W_2 \le 614 + P_A $$
$$W_3 \le 630 + P_A $$
$$W_1 \le 641 + P_B$$
$$W_2 \le 645 + P_B$$
$$W_3 \le 649 + P_B$$
\newline
$$ \text From \hspace{2mm} the \hspace{2mm} above \hspace{2mm} we \hspace{2mm} can \hspace{2mm}  see \hspace{2mm} that \hspace{2mm} W_1 - P_A \ge 622$$
\newline
$$ that \hspace{2mm} can \hspace{2mm}also \hspace{2mm} be \hspace{2mm} expressed \hspace{2mm} as \hspace{2mm} W_1 \le 622 + P_A$$
\newline
$$ \text Here \hspace{2mm} W_1 \hspace{2mm} is \hspace{2mm} considered \hspace{2mm} as \hspace{2mm} the \hspace{2mm} price \hspace{2mm} payments \hspace{2mm} being \hspace{2mm} received \hspace{2mm} at \hspace{2mm} the \hspace{2mm} origin \hspace{2mm} which \hspace{2mm} is \hspace{2mm} nothing \hspace{2mm} else, \hspace{2mm}$$ 
$$\text but \hspace{2mm} the \hspace{2mm} revenue,\hspace{2mm} whereas\hspace{2mm} P_A + 622 \hspace{2mm} is \hspace{2mm} the \hspace{2mm} money \hspace{2mm} paid \hspace{2mm} at \hspace{2mm} the \hspace{2mm} origin \hspace{2mm} at \hspace{2mm} Plant_A \hspace{3mm}$$
\newline
$$\text Therefore \hspace{2mm}  here \hspace{2mm} the \hspace{2mm} equation \hspace{2mm} will \hspace{2mm} be \hspace{2mm} MR_1 >= MC_1.$$
\newline
$$\text we \hspace{2mm}  know \hspace{2mm} that , For \hspace{2mm} a \hspace{2mm} profit \hspace{2mm} maximization, \hspace{2mm} The \hspace{2mm} Marginal \hspace{2mm} Revenue (MR)\hspace{2mm} should \hspace{2mm}be \hspace{2mm}equal\hspace{2mm} to\hspace{2mm} Marginal\hspace{2mm} Costs(MC)$$
\newline
$$ \text Therefore,\hspace{3mm}
MR_1 = MC_1$$
\newline
$$\text From \hspace{2mm} the \hspace{2mm} above\hspace{2mm} interpretation,\hspace{2mm} we\hspace{2mm} can\hspace{2mm} Observe\hspace{2mm} that,$$
$$\text The \hspace{2mm} Profit\hspace{2mm} maximization\hspace{2mm} takes\hspace{2mm} place \hspace{2mm} if\hspace{2mm} MC\hspace{2mm} is\hspace{2mm} equal\hspace{2mm} to\hspace{2mm} MR \hspace{2mm} (MC=MR).$$
\newline
***If MR < MC, We have to  lower plant costs in order to obtain the Marginal Revenue (MR).***
  
 \vspace{1mm}
 ***If MR > MC, We have to  boost manufacturing supply if we want to reach the Marginal Revenue (MR).***


