---
title: "QMM-Final Group Project-3"
author: "Manasa Chelukala"
date: '2022-12-09'
output:
  pdf_document: default
  html_document: default
---

## Project Group - 03

Manasa Chelukala

Yash Bhanushali

Swetha Kanakavalli

***No Specific Assumptions have been made to be considered,each group should have an equal choice of contribution i.e. no specific groups***

## Factors that define the success of the students

The three factors we have considered to predict the performance of the students are:

1. Course GPA - GPA of the student for a course 

2. Proficiency - Defining how proficient a student in the course.

3. Coursework - How well the student knows about the course.

## Data Collection
Course administrators should have no problem collecting student GPA's.Other factors can be collected by survey/questionnaire or by showing hands during class.


# Each group has three students out of 12 students.
```{r}
set.seed(64018)
Data_Of_the_Student <- data.frame(Course_GPA = rnorm(12, mean=0.80, sd=0.1),
                       Proficiency = sample(0:1, size=12, replace=TRUE),
                       Coursework = sample.int(5, size=12, replace=TRUE))
```


```{r}
# Ensuring max GPA of 1 and rounding to two places
library(dplyr)
Data_Of_the_Student <- Data_Of_the_Student %>% mutate(Course_GPA=if_else(Course_GPA > 1, 1, round(Course_GPA, 2)))
```


```{r}
head(Data_Of_the_Student)
```
## Decision Variables

Decision variables are members of groups.A value of $H_[i,j]$ indicates whether a student belongs to the group in which the student is jth.

## Objective Function

It is the objective of this project to maximize the chances of success for each individual group.

Since all the groups will have equal chances of success, we only need to calculate the success rate of one group: $\text{MAX} \hspace{.2cm} Z=q_1 $ letting $q_i$ represent the success rate of the ith group.

Based on the factors above, we can define the chances of success.For all j students in group i,

let $q_i = /Sigma_j / y_j + f_j + 0.2l_j$, 

where,
$y_j$ is the student's GPA, 

$f_j$ is whether they have similar prior proficiency, and 

$l_j$ is their CourseWork.

As needed, the coefficients can be adjusted.

## Constraints considered for this project
The constraints we have considered for this model are the following:

* The chances of success should be equal for all groups.

* Each group has exactly three members.

* A member must be in exactly one group at a time.
```{r}
library(lpSolveAPI)
Student_Model <- read.lp("StudentGroupProject.lp")
solve(Student_Model)

```

```{r}
get.objective(Student_Model)
```

```{r}
get.variables(Student_Model)
```
## Decisions from the Group-1,2,3,4
Below are the decisions for where each student should end up: 

Group 1: Students - 1,8,10

Group 2: Students - 2,3,5

Group 3: Students - 4,7,11  

Group 4: Students - 6,9,12
