---
title: "Assignment_4"
author: "Manasa Chelukala"
date: '2022-10-22'
output:
  pdf_document: default
  html_document: default
---
```{r}
# 'Benchmarking' package is required for running the DEA functions.
#require(Benchmarking)
#install.packages("Benchmarking")
library(Benchmarking)
```

Loading the Data
```{r}
# Create matrix for the two inputs
X <- matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2)
# Create matrix for the two outputs
Y <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000, 3500, 21000, 10500, 42000, 25000, 15000), ncol = 2)
# Name the columns of the inputs and outputs
colnames(X) <- c("Staff Hours per Day","Supplies per Day")
colnames(Y) <- c("Reimburse Patient-Days", "Privately Paid Patient-Days")
# Returning  the matrices 
print(X)
print(Y)
```
***1. Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH.***
***2. Determine the Peers and Lambdas under each of the above assumptions***

The below code will return the results of DEA using FDH method.
```{r}
# DEA code utilizing the FDH method
FDH <- rep("FDH", times = 6)
Not_Applicable <- rep(NA, times = 6)
DEA_FDH <- dea(X, Y, RTS = "FDH")
DEA_FDH_Peers <- peers(DEA_FDH)                             
DEA_FDH_Lambda <- lambda(DEA_FDH)  
print(DEA_FDH)
print(DEA_FDH_Peers)
print(DEA_FDH_Lambda)
dea.plot.isoquant(X, Y, RTS= "FDH")
# Summarize the results for addition to a summary table
DEA_FDH_Peers <- cbind(DEA_FDH_Peers, Not_Applicable, Not_Applicable)
FDH_Summary <- cbind(FDH, DEA_FDH$eff, DEA_FDH_Peers, DEA_FDH_Lambda)
colnames(FDH_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
print(FDH_Summary)
```

The below code will return the results of DEA using CRS method.
```{r}
# DEA code utilizing the CRS method
CRS <- rep("CRS", times = 6)
DEA_CRS <- dea(X, Y, RTS = "CRS")
DEA_CRS_Peers <- peers(DEA_CRS)                             
DEA_CRS_Lambda <- lambda(DEA_CRS)                            
print(DEA_CRS)
print(DEA_CRS_Peers)
print(DEA_CRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "CRS")
# Summarize the results for addition to a summary table
DEA_CRS_Lambda <- cbind(DEA_CRS_Lambda, Not_Applicable, Not_Applicable)
CRS_Summary <- cbind(CRS, DEA_CRS$eff, DEA_CRS_Peers, DEA_CRS_Lambda)
colnames(CRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
CRS_Summary <- as.data.frame(CRS_Summary)
CRS_Summary
```
The below code will return the results of DEA using VRS method.
```{r}
# DEA code utilizing the VRS method
VRS <- rep("VRS", times = 6)
DEA_VRS <- dea(X, Y, RTS = "VRS")
DEA_VRS_Peers <- peers(DEA_VRS)                             
DEA_VRS_Lambda <- lambda(DEA_VRS)                            
print(DEA_VRS)
print(DEA_VRS_Peers)
print(DEA_VRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "VRS")
# Summarize the results for addition to a summary table
DEA_VRS_Lambda <- cbind(DEA_VRS_Lambda, Not_Applicable)
VRS_Summary <- cbind(VRS, DEA_VRS$eff, DEA_VRS_Peers, DEA_VRS_Lambda)
colnames(VRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
VRS_Summary <- as.data.frame(VRS_Summary)
VRS_Summary
```

The below code will return the results of DEA using IRS method.
```{r}
# DEA code utilizing the IRS method
IRS <- rep("IRS", times = 6)
DEA_IRS <- dea(X, Y, RTS = "IRS")
DEA_IRS_Peers <- peers(DEA_IRS)                             
DEA_IRS_Lambda <- lambda(DEA_IRS)                            
print(DEA_IRS)
print(DEA_IRS_Peers)
print(DEA_IRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "IRS")
# Summarize the results for addition to a summary table
DEA_IRS_Lambda <- cbind(DEA_IRS_Lambda, Not_Applicable)
IRS_Summary <- cbind(IRS, DEA_IRS$eff, DEA_IRS_Peers, DEA_IRS_Lambda)
colnames(IRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
IRS_Summary <- as.data.frame(IRS_Summary)
IRS_Summary
```

The below code will return the results of DEA using DRS method.
```{r}
# DEA code utilizing the DRS method
DRS <- rep("DRS", times = 6)
DEA_DRS <- dea(X, Y, RTS = "DRS")
DEA_DRS_Peers <- peers(DEA_DRS)                             
DEA_DRS_Lambda <- lambda(DEA_DRS)                            
print(DEA_DRS)
print(DEA_DRS_Peers)
print(DEA_DRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "DRS")
# Summarize the results for addition to a summary table
DEA_DRS_Lambda <- cbind(DEA_DRS_Lambda, Not_Applicable, Not_Applicable)
DRS_Summary <- cbind(DRS, DEA_DRS$eff, DEA_DRS_Peers, DEA_DRS_Lambda)
colnames(DRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
DRS_Summary <- as.data.frame(DRS_Summary)
DRS_Summary
```

The below code will return the results of DEA using FRH/ADD method.
```{r}
# DEA code utilizing the ADD method
ADD <- rep("ADD", times = 6)
DEA_ADD <- dea(X, Y, RTS = "ADD")
DEA_ADD_Peers <- peers(DEA_ADD)                             
DEA_ADD_Lambda <- lambda(DEA_ADD)                            
print(DEA_ADD)
print(DEA_ADD_Peers)
print(DEA_ADD_Lambda)
# Summarize the results for addition to a summary table
DEA_ADD_Peers <- cbind(DEA_ADD_Peers, Not_Applicable, Not_Applicable)
ADD_Summary <- cbind(ADD, DEA_ADD$eff, DEA_ADD_Peers, DEA_ADD_Lambda)
colnames(ADD_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
ADD_Summary <- as.data.frame(ADD_Summary)
ADD_Summary
```
***3. Summarize your results in a tabular format***
```{r}
# Combine all of the method summary tables into one large summary table for each method
Summary_Table <- rbind(FDH_Summary, CRS_Summary, VRS_Summary, IRS_Summary, DRS_Summary, ADD_Summary)
# Return the summary table for review
print(Summary_Table)
```
***4. Compare and contrast the above results***

As shown in the summary table, all six DMU's return FRH and FDH efficiency values of 1.0, along with identical peer and lambda values.

In the CRS method, DMU[1:4] is efficient at 1.0.

In the VRS method  DMU[1:5] is efficient at 1.0.

In the IRS method  DMU[1:5] is efficient at 1.0, and

In the DRS method  DMU[1:4] is efficient at 1.0.

All of these less efficient DMU's had a Peer[1] and Peer [2] value of 1 and 2, respectively; 

Depending on the method,However, the Peer[3] value was either 4 or 5. 

Furthermore, all methods were relatively close in terms of relative weights (lambdas).
